Contracts for unions and intersections are hard for Nickel

### 2021-06-01 paper.tex
Typo
Fit error message example within the line size

Figure~\ref{fig:contract-reporting-wo} and Figure~\ref{fig:contract-reporting-w}
give an example of a situation where adding a simple contract annotation
\nickel{Str -> Str} to a function greatly improves the error message . In the
original program of Figure~\ref{fig:contract-reporting-wo}, the
\nickel{catHosts} function takes a string argument, append it to a list that is
then folded. However, the programmer forgot one parameter when calling to
\nickel{makeHost}, thus passing a partially applied function instead of a string
to \nickel{catHosts}. Because this argument is put in a list and folded, the
error is raised later on and points to inside the code of \nickel{catHosts} and
\nickel{makeHost}, which may be totally unknown to the caller.

@@

\begin{lstlisting}[title={Error message with contract},frame=none,numbers=none]
error: Blame error: contract broken by the caller.
  |  Str -> Str
  |  --- expected type of the argument [(*@{\ldots}@*)]
[(*@{\ldots}@*)]
1 | let catHosts | Str -> Str = fun last =>
  |                ^^^^^^^^^^ bound here
[(*@{\ldots}@*)]
6 | catHosts (makeHost "google")
  | ---------------------------- (2) calling <func>
\end{lstlisting}
  \end{center}
\caption{Error reporting with contract}
\label{fig:contract-reporting-w}
\end{figure}

>>>>

Figure~\ref{fig:contract-reporting-wo} and Figure~\ref{fig:contract-reporting-w}
give an example of a situation where adding a simple contract annotation
\nickel{Str -> Str} to a function greatly improves the error message. In the
original program of Figure~\ref{fig:contract-reporting-wo}, the
\nickel{catHosts} function takes a string argument, append it to a list that is
then folded. However, the programmer forgot one parameter when calling to
\nickel{makeHost}, thus passing a partially applied function instead of a string
to \nickel{catHosts}. Because this argument is put in a list and folded, the
error is raised later on and points to inside the code of \nickel{catHosts} and
\nickel{makeHost}, which may be totally unknown to the caller.

@@

\begin{lstlisting}[title={Error message with contract},frame=none,numbers=none, basicstyle=\footnotesize\ttfamily]
error: Blame error: contract broken by the caller.
  |  Str -> Str
  |  --- expected type of the argument [(*@{\ldots}@*)]
[(*@{\ldots}@*)]
1 | let catHosts | Str -> Str = fun last =>
  |                ^^^^^^^^^^ bound here
[(*@{\ldots}@*)]
6 | catHosts (makeHost "google")
  | --------------------------- (2) calling <func>
\end{lstlisting}
  \end{center}
\caption{Error reporting with contract}
\label{fig:contract-reporting-w}
\end{figure}
